Capitalized Title Here

### 2021-02-06 CMPSpaper_writing/CMPSpaper_writing.Rmd
added a figure and numbers in the example

The automated framework we used in this paper was proposed by Hare and Hofmann in 2017 [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS?]. In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` packages `x3ptools`[cite?] and `bulletxtrctr`[cite?]. `x3ptools` can be used to process x3p files. In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`). Figure x.a shows a bullet land impression scan of a processed x3p file. The raised portion of the surface are groove impressions, and the vertical striation marks between the groove impressions are what we are interested in, called a land impression. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression. `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`). Figure x shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression. `bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept. With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [Cleveland 1979?] and can obtain the bullet signature. Figure x illustrates this framework. Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors. Note that NIST researchers used a different way of getting the bullet signatures in their paper [cite?].

@@

We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons. (TOBE UPDATED !!!)

```{r}
#      [,1] [,2] [,3] [,4] [,5] [,6]
# [1,]    2    5    3    4    3    2
# [2,]    2    2   13    1    1    1
# [3,]    1    1    2   11    2    2
# [4,]    2    1    1    1   10    1
# [5,]    1    2    1    2    2   15
# [6,]   14    2    2    2    1    1
```

@@

[an example that explains cmps.max and cmps.maxbar]

In this example, the $\mathrm{CMPS_{max}}=?$ and $\mathrm{\overline{CMPS}_{max}}=()/6=$.

@@

Figure x shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252. Although the CMPS scores we found here are not exactly the same as those presented in the [original paper] since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising. For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM). Table x shows some summary statistics.

@@

```{r, echo=FALSE, out.width="400px"}
# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
```

[table ???]

Figure x shows the results for Hamby set 44. Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged. Table x shows some summary statistics for Hamby set 44.

@@

@@

Figure x shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`. We can see that the separation between KM comparisons and KNM comparisons is increased. This shows that the parameters used in the CMPS algorithm can affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.

@@

For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures/profiles; however, in this example we used `span1=0.75` and changed the characteristic of those profiles. As we can see in figure x, this change also affects the CMPS results.

@@

<!-- Present results: -->

* apply it to Hamby252 -> able to reproduce results in NIST paper qualitatively
  - exclude some (?) scans because they are bad -> go further in Conclustion
  - [CHECK] Did researchers exclude those scans in NIST paper? Yes, they removed outliers
<!-- * apply it to another dataset, which have a different resolution -->
<!--   - potential issues -> go further in Conclusion -->
<!--   - need to use a different set of parameters -->

@@

(Our opinions)

>>>>

The automated framework we used in this paper was proposed by Hare and Hofmann in 2017 [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS?]. In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` packages `x3ptools`[cite?] and `bulletxtrctr`[cite?]. `x3ptools` can be used to process x3p files. In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`). Figure 1(a) shows a bullet land impression scan of a processed x3p file. The raised portion of the surface are groove impressions, and the vertical striation marks between the groove impressions are what we are interested in, called a land impression. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression. `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`). Figure 1(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression. `bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept. With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [Cleveland 1979?] and obtain the bullet signature. Figure 1 illustrates this framework. Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors. Note that NIST researchers used a different way of getting the bullet signatures in their paper [cite?].

figure 1:

```{r, echo=FALSE, out.width="400px"}
knitr::include_graphics("img/figure1.png", dpi = 100)
```

@@

We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.

```{r}
#      [,1] [,2] [,3] [,4] [,5] [,6]
# [1,]    2    3    2    3    1    2
# [2,]    2    1   17    1    2    3
# [3,]    1    1    3   14    2    2
# [4,]    2    1    1    1   10    1
# [5,]    2    2    1    1    1   15
# [6,]   16    3    1    2    1    1
```

@@

```{r}
#      [,1] [,2] [,3] [,4] [,5] [,6]
# [1,]    2    3    2    3    1    2
# [2,]    2    1   17    1    2    3
# [3,]    1    1    3   14    2    2
# [4,]    2    1    1    1   10    1
# [5,]    2    2    1    1    1   15
# [6,]   16    3    1    2    1    1
```

In this example, the $\mathrm{CMPS_{max}}=17$ and $\mathrm{\overline{CMPS}_{max}}=(16+3+17+14+10+15)/6=12.5$.

@@

Figure 2 shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252. Although the CMPS scores we found here are not exactly the same as those presented in the [original paper] since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising. For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM). Table x shows some summary statistics.

@@

<!-- this is figure 2 -->
```{r, echo=FALSE, out.width="400px"}
# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
```

table 1:

<!-- |Parameters             | $\mathrm{CMPS_{max}}$ - KNM's max| $\mathrm{CMPS_{max}}$ - KM's min| $\mathrm{\overline{CMPS}_{max}}$ - KNM's max| $\mathrm{\overline{CMPS}_{max}}$ - KM's min| -->
<!-- |:----------------------|---------------------------------:|--------------------------------:|--------------------------------------------:|-------------------------------------------:| -->
<!-- |span1=0.25, (5, 3, 1)  |                                 7|                               10|                                       3.6000|                                      6.6667| -->
<!-- |span1=0.25, (10, 6, 1) |                                 9|                               13|                                       4.8333|                                      9.1667| -->
<!-- |span1=0.75, (5, 3, 1)  |                                 6|                               11|                                       3.1667|                                      6.6000| -->

```{r, echo=FALSE}
# library(knitr)
# library(kableExtra)
# rtt <- readRDS("summary_table.rds")
# colnames(rtt) <- 
rtt <- data.frame(parameters = c("span1=0.25, (5, 3, 1)", "span1=0.25, (10, 6, 1)", "span1=0.75, (5, 3, 1)"),
                  p1 = c(7,9,6),
                  p2 = c(10, 13, 11),
                  p3 = c(3.6, 4.833, 3.167),
                  p4 = c(6.667, 9.167, 6.6))

knitr::kable(rtt, 
             row.names = FALSE, digits = 4,
             col.names = c("Parameters",
                           "$\\mathrm{CMPS_{max}}$ - KNM's max",
                           "$\\mathrm{CMPS_{max}}$ - KM's min",
                           "$\\mathrm{\\overline{CMPS}_{max}}$ - KNM's max",
                           "$\\mathrm{\\overline{CMPS}_{max}}$ - KM's min")) 
```

Figure 3 shows the results for Hamby set 44. Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged. Table 1 shows some summary statistics for Hamby set 44.

@@

<!-- this is figure 3 -->

@@

Figure 4 shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`. We can see that the separation between KM comparisons and KNM comparisons is increased. This shows that the parameters used in the CMPS algorithm can affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.

<!-- this is figure 4 -->

@@

For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures/profiles; however, in this example we used `span1=0.75` and changed the characteristic of those profiles. As we can see in figure 5, this change also affects the CMPS results.

<!-- this is figure 5 -->

@@

@@
